%-------------------------
% Resume in Latex (Updated with New Skills)
% Author : Maneesh V
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage[utf8]{inputenc}

% Adjust margins
\geometry{left=0.5in, top=0.4in, right=0.5in, bottom=0.4in, footskip=.3in}

% Colors
\definecolor{airforceblue}{RGB}{93, 138, 168}
\definecolor{cvblue}{HTML}{0E5484}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}

% Global list spacing (KEY FIX)
\setlist[itemize]{itemsep=0pt, topsep=0pt, parsep=0pt}

% Custom commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[left=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.8em]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
\newcommand{\resumeItemSmall}[1]{\item \small{#1}}

% Fonts
\usepackage{CormorantGaramond}
\usepackage{charter}

% Section formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Subheadings
\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large#1} & \textbf{\small #2} \\
    \textit{\large#3} & \textit{\small #4} \\
  \end{tabular*}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\large#1} & \textbf{\small #2}\\
  \end{tabular*}
}

%---------- RESUME ----------
\begin{document}

\begin{center}
    {\huge \textbf{Maneesh V}} \\ \vspace{3pt}
    {+91 7358112574} •
    \href{mailto:maneeshprog@gmail.com}{maneeshprog@gmail.com} •
    \href{https://www.linkedin.com/in/maneesh-gee-5a2303256/}{LinkedIn} •
    \href{https://github.com/ManeeshProg}{GitHub} •
    \href{https://notmaneesh23.github.io/PortfolioDeploy/#}{Portfolio}
\end{center}

\vspace{4pt}
\noindent
Machine Learning Engineer specializing in \textbf{Computer Vision and LLM-based automation}, with hands-on experience
building \textbf{real-time visual inspection and safety analytics systems} for operational environments
across edge and cloud platforms.

%----------- EDUCATION -----------
\section{\color{airforceblue}EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading
    {St. Joseph's College of Engineering, Chennai}{May 2022 – Present}
    {B.Tech – Artificial Intelligence and Machine Learning}{CGPA: 8.40}
\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------
\section{\color{airforceblue}WORK EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
  {Computer Vision Engineer (Intern) – MacV AI}{June 2025 – Present}
  {Production ML Systems for Intelligent Visual Inspection}{}
\resumeItemListStart
\resumeItemSmall{Developed and productionized \textbf{real-time computer vision pipelines} for safety analytics and visual inspection using \textbf{YOLO} and \textbf{DeepStream}, supporting live RTSP video streams.}
\resumeItemSmall{Implemented multi-service inference workflows handling concurrent camera streams, enabling low-latency object detection, tracking, and rule-based compliance checks.}
\resumeItemSmall{Designed a \textbf{place-matching system} combining object detection with \textbf{DINOv2 embeddings} and \textbf{FAISS vector search} to identify key locations and contextual regions from video feeds.}
\resumeItemSmall{Built modular backend services using \textbf{FastAPI} to expose multiple AI models via unified, production-ready APIs.}
\resumeItemSmall{Optimized inference performance through \textbf{ONNX conversion} and model quantization; integrated deployments into CI/CD pipelines across \textbf{AWS} and \textbf{Azure}.}
\resumeItemListEnd

\resumeSubheading
  {Research Intern – IIITDM Chennai}{May 2024 – July 2024}
  {Machine Learning for Semiconductor Manufacturing Optimization}{}
\resumeItemListStart
  \resumeItemSmall{Developed predictive machine learning models to analyze complex VLSI design parameters, enabling early identification of manufacturing yield and reliability risks.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- TECHNICAL SKILLS -----------
\section{\color{airforceblue}TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
  \item \textbf{Computer Vision:} PyTorch, YOLO, DeepStream, OpenCV, Object Detection, Tracking, Segmentation, DINOv2
  \item \textbf{Generative AI \& LLMs:} Hugging Face, RAG Pipelines, Vector Databases, Prompt Engineering
  \item \textbf{Production \& Deployment:} FastAPI, ONNX, TensorRT, Quantization, Docker, CI/CD, AWS, Azure, Edge AI
  \item \textbf{Infrastructure \& DevOps:} Terraform, Kubernetes, GitHub Actions, Cloud Networking
  \item \textbf{Programming Languages:} Python, Java, C
\end{itemize}

%----------- PROJECTS -----------
\section{\color{airforceblue}PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Distributed Multi-Camera Visual Inspection \& Monitoring System}}{}
\resumeItemListStart
  \resumeItemSmall{Designed and deployed a \textbf{distributed computer vision--based visual inspection system} with fine-tuned models for object detection, tracking, and event recognition across multiple camera streams.}
  \resumeItemSmall{Built \textbf{real-time video inference pipelines} with camera health monitoring and centralized analytics for scalable, low-latency operation.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{Domain-Specific LLM System for Automated Technical Analysis (PyPI)}}{}
\resumeItemListStart
  \resumeItemSmall{Developed and published a \textbf{PyPI package} for automated technical analysis of Git commits using LLMs and vector-based retrieval.}
  \resumeItemSmall{Specialized the LLM pipeline for \textbf{Computer Vision workflows}, enabling detection of CV-specific issues such as data leakage, preprocessing errors, and inference inefficiencies.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{Freelance Cloud \& AI Deployments (5+ Projects)}}{}
\resumeItemListStart
  \resumeItemSmall{Delivered \textbf{5+ production freelance deployments}, building and operating scalable, production-ready systems for diverse client use cases.}
  \resumeItemSmall{Provisioned and managed \textbf{AWS cloud infrastructure} with automated deployments, environment-specific configuration, and operational best practices.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%----------- ACHIEVEMENTS & CERTIFICATIONS -----------
\section{\color{airforceblue}ACHIEVEMENTS \& CERTIFICATIONS}
\begin{itemize}[leftmargin=0in, label={}]
  \item \textbf{2$\times$ Winner, IIT Madras Shaastra ML Challenge} — recognized for strong performance in applied machine learning problem-solving.
  \item \textbf{ServiceNow Certified System Administrator (CSA)}
  \item \textbf{AWS Certification} — In Progress
\end{itemize}
\end{document}
